Measuring security performance in the Android ecosystem

### 2015-06-03 ccs.tex
Fill in abstract

\begin{abstract}
We find there is significant variability in the timely delivery of security updates across different device manufacturers and mobile network operators, and we define a security metric to rank the performance of device manufacturers and network operators in our data set.
TODO
\end{abstract}

>>>>

\begin{abstract}
The security of Android is severely damaged by the lack of security updates for known critical vulnerabilities  being shipped to devices.
We find there is significant variability in the timely delivery of security updates across different device manufacturers and mobile network operators, and we define a security metric to rank the performance of device manufacturers and network operators in our data set.
This provides the comparable data required for purchasers to determine which device manufacturers and network operators to use and hence incentives them to ship security updates.
\end{abstract}
